A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-01-26 journal/example.tex
done

\begin{figure*}
\begin{code}
 01  void compile(program: feature list, optimizeLevel: int) \{
 02    internalRepresentation = initInternalRep(program);
 03    if optimizeLevel > 0: \{
 04       if feature1 in program:
 05          if feature2 in program:
 06             corrupt(internalRepresentation);
 07       if optimizeLevel > 1: \{
 08          if feature3 in program:
 09             if feature4 not in program:
 10                corrupt(internalRepresentation);
 11          if feature5 in program:
 12             if feature6 in program:
 13                corrupt(internalRepresentation);
 14       \}
 15    \}
 16    /* Will produce wrong code if structure has been corrupted */
 17    generateCode(internalRepresentation);
\end{code}
\caption{A toy ``optimizing compiler'' with multiple bugs}
\label{fig:example}
\end{figure*}

>>>>

\begin{figure*}
\begin{code}
 01  void compile(program: feature list, optimizeLevel: int) \{
 02    internalRepresentation = initInternalRep(program);
 03    if optimizeLevel > 0: \{
 04       if feature1 in program:
 05          if feature2 in program:
 06             corrupt(internalRepresentation);
 07       if optimizeLevel > 1: \{
 08          if feature3 in program:
 09             if feature4 not in program:
 10                corrupt(internalRepresentation);
 11          if feature5 in program:
 12             if feature6 in program:
 13                corrupt(internalRepresentation);
 14       \}
 15    \}
 16    /* Will produce wrong code if corrupt called */
 17    generateCode(internalRepresentation);
\end{code}
\caption{A toy ``optimizing compiler'' with multiple bugs}
\label{fig:example}
\end{figure*}
